Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-21 paper.tex
Add note about NACA profiles
Define CFT earlier

The performance and wake characteristics of cross-flow (vertical-axis) turbines
depend on turbine solidity, blade profile (lift/drag, dynamic stall at reduced
frequency of turbine rotation, symmetry, thickness, camber), blade pitch, number
of blades, strut drag, operational parameters, such as tip speed ratio; and on
the Reynolds number \cite{Para2002}. Note that an average blade chord Reynolds
number, $Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$, can be expressed
in terms of tip speed ratio $\lambda = \omega R/ U_\infty$, where $U_\infty$ is
the free stream velocity, $c$ is the blade chord length, $\nu$ is the fluid
kinematic viscosity, $\omega$ is the rotor's angular velocity, and $R$ is the
rotor radius. The value of $\lambda$ at which a turbine reaches peak performance
in general decreases with turbine solidity $Nc/(\pi D)$ \cite{Templin1974},
which allows for the use of a simpler Reynolds number based on turbine diameter
$Re_D = U_\infty D/\nu$.

@@

The UNH-RVAT turbine has three blades made from \hl {NACA} 0020 profiles
%please define NACA and add the information of Manufacturer, City, Country
  with a 0.14 m
chord. The~blades are mounted at mid-chord w.r.t. the turbine axis, and the
turbine has a height (blade span) of 1 m and a diameter of 1 m; \textit{cf}.
Figure~\ref{fig:turbine}. The blockage ratio produced by the rotor's frontal
area is 11\%, which we decided not to correct for, as reliable methods are
not yet agreed upon for \hl {CFTs} %please define
\cite{Cavagnaro2014}. As such, blockage should be
taken into account when using these data for model validation, \emph{i.e.}, the
experimental domain should be mimicked. The rotor has a relatively high solidity
$Nc/(\pi D) = 0.13$ and a large chord-to-radius ratio $c/R = 0.28$. A CAD model of
the turbine is available from \cite{Bachant2014-RVAT-CAD}.

>>>>

The performance and wake characteristics of cross-flow (vertical-axis) turbines
(CFTs) depend on turbine solidity, blade profile (lift/drag, dynamic stall at
reduced frequency of turbine rotation, symmetry, thickness, camber), blade
pitch, number of blades, strut drag, operational parameters, such as tip speed
ratio; and on the Reynolds number \cite{Para2002}. Note that an average blade
chord Reynolds number, $Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$,
can be expressed in terms of tip speed ratio $\lambda = \omega R/ U_\infty$,
where $U_\infty$ is the free stream velocity, $c$ is the blade chord length,
$\nu$ is the fluid kinematic viscosity, $\omega$ is the rotor's angular
velocity, and $R$ is the rotor radius. The value of $\lambda$ at which a turbine
reaches peak performance in general decreases with turbine solidity $Nc/(\pi D)$
\cite{Templin1974}, which allows for the use of a simpler Reynolds number based
on turbine diameter $Re_D = U_\infty D/\nu$.

@@

% Note below: NACA is not a manufacturer, but a very common type of foil profile

The UNH-RVAT turbine has three blades made from NACA 0020 profiles with a 0.14 m
chord. The~blades are mounted at mid-chord w.r.t. the turbine axis, and the
turbine has a height (blade span) of 1 m and a diameter of 1 m; \textit{cf}.
Figure~\ref{fig:turbine}. The blockage ratio produced by the rotor's frontal
area is 11\%, which we decided not to correct for, as reliable methods are not
yet agreed upon for CFTs \cite{Cavagnaro2014}. As such, blockage should be taken
into account when using these data for model validation, \emph{i.e.}, the
experimental domain should be mimicked. The rotor has a relatively high solidity
$Nc/(\pi D) = 0.13$ and a large chord-to-radius ratio $c/R = 0.28$. A CAD model
of the turbine is available from \cite{Bachant2014-RVAT-CAD}.
